\documentclass{article}[11pt]

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{yfonts,color}
\usepackage{lettrine}

\def\initdefault{yinit}

\linespread{1}
\setlength\parindent{0pt}

\begin{document}

{\frakfamily\fraklines \lettrine[lines=2]{\yinipar{O}}{ur} plan.
We shall regularly useth tuesday to meeteth up and w'rk on our projecteth f'r the full day.  Throughout the week we shall w'rk on the individual tasks we has't designat'd f'r both of us. \\
 
We shall break with our approach to the abstract problems and decideth on strategies togeth'r, aft'r which th're art typically sev'ral distinct areas f'r implementation yond we can divideth between us f'r the weekly w'rkload.  We can then marryeth these implementations togeth'r on the following tuesday of each week. \\
 
Regarding our approach to the projecteth, we shall proce'd by creating this simplest possible chex'rs-playing-ai yond w'rks, and then t'ratively extendeth this, piece-by-piece, rath'r than going f'r the smartest possible ai straight hence. \\
 
At the bareth minimum, we shall beginneth by implementing a simple minimax alg'rithm, using a simple evaluation function.  Aft'r each t'ration, we shall playeth 'gainst t to figure out t's most gross in sense weaknesses, and tryeth to improveth our evaluation function to a reasonable extent. \\
 
Once we has't exhaust'd these simple improvements, we shall expl're m're sophisticat'd improvements, such as machine learning (again beginning simply, and t'ratively adding sophistication). \\
 
The projecteth is due on the 21st of may - just ov'r 4 weeks hence.  Below lists deadlines f'r our oth'r subjects.
\begin{itemize}
    \item 30/04 - Graph Theory (Billy)
    \item 03/05 - Software Modelling and Design (Billy and Luca)
    \item 10/05 - Algebra (Billy)
\end{itemize}



}

\end{document}